%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}				
\usepackage{hyperref}
\usepackage{fontawesome5}

% Setup hyperref package, and colours for links
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Deepak Mangal} \\[7.5pt]
\href{https://github.com/deepakagrawal3103}{\raisebox{-0.05\height}\faGithub\ deepakagrawal3103} \ $|$ \ 
\href{https://www.linkedin.com/in/deepak-mangal-695639279/}{\raisebox{-0.05\height}\faLinkedin\ Deepak Mangal} \ $|$ \ 
\href{mailto:deepak3103agrawal@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ deepak3103agrawal@gmail.com} \ $|$ \ 
\href{tel:+91623274465}{\raisebox{-0.05\height}\faMobile \ +91 6232744465} \\
\end{tabularx}
\noindent\rule{\linewidth}{0.5pt} % Horizontal line after title

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------
\section{Work Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\multicolumn{2}{@{}X@{}}{Web Developer Intern \hfill 2023} \\ 
\multicolumn{2}{@{}X@{}}{
- Developed a static Amazon website clone using HTML and CSS, enhancing skills in front-end design and user interface.
- Collaborated on a C++ scientific calculator project, implementing 15+ complex mathematical functions.
- Contributed to a transport-sharing app concept for Smart India Hackathon, focusing on real-time problem-solving.
- Participated in a college hackathon, working closely with senior developers, gaining valuable mentorship and experience.
- Gained hands-on experience in teamwork, adaptability, and effective communication in a fast-paced development environment.
}  \\ 
\end{tabularx}
\noindent\rule{\linewidth}{0.5pt} % Horizontal line after work experience

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{tabularx}{\linewidth}{ @{}l X@{} }
\textbf{Projects} & \hfill \href{https://github.com/deepakagrawal3103}{click here} \\[3.75pt]

\textbf{Amazon Clone:} & Created a static website clone of Amazon using HTML and CSS, focusing on layout design and user experience. The project features 50+ product listings, enhancing my front-end development skills and improving user interaction. \href{https://deepakagrawal3103.github.io/amazonclone/}{click here} \\[3pt]

\textbf{Scientific Calculator:} & Developed a C++ scientific calculator as part of a team project, implementing 15+ mathematical functions including addition, subtraction, and logarithms. Enhanced coding skills through collaboration with 3 team members, gaining hands-on experience with object-oriented programming concepts. \\[3pt]

\textbf{Notes App:} & Designed a notes application using HTML, CSS, and JavaScript for creating and managing notes. The app supports 100+ notes with local storage for persistent access, enhancing my JavaScript and web development skills. Users can easily create, edit, and delete notes for better organization and productivity. \href{https://deepakagrawal3103.github.io/Notes-App/}{click here} \\

\end{tabularx}
\noindent\rule{\linewidth}{0.5pt} % Horizontal line after projects

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2023-27 - (present) & B.Tech in Computer Science \\ 
                  & \textbf{Sushila Devi Bansal College of Technology, Indore} \hfill \normalsize (CGPA: 7.45) \\

2023 & Class 12th, Padmaja Higher Secondary School, Dewas \hfill (77\%) \\ 

2021 & Class 10th, Padmaja Higher Secondary School, Dewas \hfill (89\%) \\ 
\end{tabularx} 
\noindent\rule{\linewidth}{0.5pt} % Horizontal line after education

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Programming Languages} & \normalsize{HTML, CSS, C++, C (beginner)} \\

\textbf{Frameworks \& Tools} & \normalsize{JavaScript (basic), Git, version control} \\

\textbf{Soft Skills} & \normalsize{Team collaboration, effective communication, adaptability, problem-solving} \\

\textbf{Technical Skills} & \normalsize{Database management (SQL), Web development (React), Time management, attention to detail} \\ 
\end{tabularx}
\noindent\rule{\linewidth}{0.5pt} % Horizontal line after skills

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
